Efficiently stable presentations from error-correcting codes

### 2023-07-10 efficient_stability.tex
cleared some comments, responded to some others

  A \emph{tracial von Neumann algebra} is a pair $(\mM,\tau)$ of a von Neumann algebra $\mM$ together with a normal faithful tracial state $\tau$ on $\mM$, which we often refer to as the \emph{trace}. The main example of interest is $\mM=M_n(\C)$, the algebra $n\times n$ complex matrices, with $\tau$ the dimension-normalized trace, which we denote $\tr(M)=\frac{1}{n}\Tr(M)$. 	We write $\|x\|_2=\tau(x^*x)^{1/2}$ for the $2$-norm on $\mM$. \hnote{sometimes we use $\| \cdot \|_\tau$ below, which one should we use?}\tnote{Ah yes sorry. I prefer $\|\cdot\|_\tau$}

@@

\begin{definition}\label{def:eff-stab}
Let $G = \langle S:R\rangle $ be a finitely presented group. Let $\mC$ be a class of tracial von Neumann algebras. Let $\mu_S$ be a distribution on $S$ and $\mu_R$ a distribution on $R$. For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ we say that \hnote{added, to make it clear that it's the presentation that's stable } the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,\mC)$-stable if for every $(\cM,\tau)$ in $\mC$, every $(\eps,\mu_R)$-almost homomorphism of $G$ is $(\delta(\eps),\mu_S)$-close to a unitary representation of $G$ on some $(\mN,\tau^\mN)\in \mC$. \tnote{added:} We refer to the function $\delta$ as the ``modulus of stability'' of the presentation.
\end{definition}

@@

\begin{theorem}\label{thm:gh}
Let $G$ be a finite group and $\mC$ the class of all tracial von Neumann algebras. Let $\mu_S$ and $\mu_R$ be the uniform distribution on $S=G$ and $R=\{ g\cdot h \cdot (gh)^{-1}=e \}$ respectively. Then $G=\langle S:R\rangle$ is $(O(\eps),\mu_S,\mu_R,\mC)$-stable.  \hnote{$U_S,U_R$ may not be the best notation, as similar names are used for unitaries e.g., in the next theorem. Maybe just say $\mu_S,\mu_R$ are uniform?}\tnote{ok, fixed}
\end{theorem}

@@

As one would naturally expect, the dependence of $\delta_k$ on $k$ depends on the girth of $\Z_2^k$ for the presentation~\eqref{eq:z2-efficient}. By expressing each element of $\Z_2^k$ as a product of generators in the natural way, applying Corollary~\ref{cor:lin-test} it is possible to show that $\delta_k=O(k^2\eps)$ in Lemma~\ref{lem:eff-z2}. With more work one can get $\delta_k=O(k\eps)$, see~\cite[Theorem 3.2]{chao2017overlapping}. This is nearly tight, as shown in~\cite{chao2017overlapping}. In the next section we will obtain presentations of $\Z_2^k$ that have a much better size/modulus tradeoff. \hnote{What does modulus mean?}\tnote{I added in Definition~\ref{def:eff-stab}}

We end with a non-Abelian group that plays an important role in applications in quantum information, the \emph{Pauli group}. For an integer $k\geq 1$,  the Pauli group $\pauli_k$ can be defined as follows. Let $\gamma: \Z_2^k\times \Z_2^k \to \{-1,1\}$ be given by $\gamma(a,b)=(-1)^{a\cdot b}$. Then $\pauli_k$ is the central extension of $\Z_2^k\times \Z_2^k$ by $\{-1,1\}$ given by $\gamma$. Alternatively, $\pauli_k$ is the group generated by the Pauli matrices $\sigma_X(a)$, $\sigma_Z(b)$ introduced in~\eqref{eq:def-pauli-2}.
It is also known as the Heisenberg group 
\[ H_{2k+1} = \left \{ \begin{pmatrix} 1 & a & c \\ 0 & I_{k \times k} & b \\ 0 & 0 & 1 \end{pmatrix} \right\}\subseteq {\mathrm{GL}}_{k+2}(\F_2)\;.\]
\hnote{what's the $1_k$ in the middle?}\tnote{$k\times k$ identity. Is it better now?}
 Concretely, %we label elements of the Pauli group as triples $(c,a,b)$ 
\hnote{is this right? There should be an option to ``turn $J$ off'' right?}\tnote{oh yes sorry. Anyways this was confusing, I removed it}
% where $c\in\{0,1\}$ and $a,b\in\Z_2^k$, and 
we consider the following presentation for the Pauli group:
\begin{align*}
 \pauli_k \,=\, \big\langle \{J\}\cup  \{(a,b): a,b\in \Z_2^k\} &: a^2=b^2=J^2=e,\; [a,J]=[b,J]=e,\\
&\qquad  (a,b)(a',b') = J^{a\cdot b'} (a',b')(a,b) \; \quad \forall a,b\big\rangle\;.
\end{align*}
\hnote{should the $J$ and $(a,b)$ be triples instead? (given the sentence about labelling Pauli group as triples...)}\tnote{no, they're generators; see above}
This presentation is not quite the exhaustive presentation (it has $2^{2k}+1$ generators, whereas $|\pauli_k|=2^{2k+1}$), but it is not far from it.  
Applying Theorem~\ref{thm:gh} we obtain the following consequence.%, which we again state only for the case of a subclass of approximate homomorphisms and the class of finite-dimensional matrix algebras\tnote{again, not sure what we want ultimately}.

@@

For $q$ a prime power and $n,k,d$ integer, a linear $[n,k,d]_q$ code $\code$ \hnote{changed to curly script C to avoid clashing with $\mC$, which was used as notation for vNAs} is a $k$-dimensional subspace of $\F_q^n$ such that for all $x\in \code$ such that $x\neq 0$, the Hamming weight $|x|$ (i.e. the number of nonzero coordinates of $xs$) is at least $d$. The parameter $n$ is called the \emph{length} of the code, $k$ its \emph{dimension} and $d$ its \emph{distance}. A code can be specified by a \emph{parity check matrix} $h\in \F_q^{m\times n}$ such that $\code = \ker h$.

For the remainder of this section we specialize the discussion to the case where $q=2$. 
A parity check matrix for a code of dimension $k$ implies a presentation in the following way. Introduce $n$ generators $S=\{x_1,\ldots,x_n\}$. Each of the generators is required to be an involution: $x_i^2=e$. For each row $i\in \{1,\ldots,m\}$ of the parity check matrix $h$, introduce a relation 
\[ R_i\,:\; \prod_{1\leq j \leq n} x_j^{h_{ij}}=e \]
that ``verifies'' the parity check associated with the $i$-th row of $h$. Finally, to guarantee that $R_i$ is independent of the order in which the $x_j$ are multiplied, whenever $j\neq j'$ are such that $h_{ij}$ and $h_{ij'}$ are both nonzero we require that $x_j$ and $x_{j'}$ commute. This can be written succinctly using a relation 
\[ R'_{ijj'}\,:\; [x_j,x_{j'}]^{h_{ij} h_{ij'}}=e\;.\]
The presentation obtained in this way defines a group $G=G(h)$ as 
\begin{equation}\label{eq:def-gh-pres}
 G(h) \,=\, \big\langle x_1,\ldots,x_n \,:\, x_j^2=e\,,\; R_i\,,\; R'_{ijj'}\,,\quad \forall 1\leq i\leq m,\, 1\leq j< j' \leq n\big\rangle\;.
\end{equation}
\hnote{should it be $1 \leq i \leq m$, $1 \leq j < j' \leq n$?}\tnote{Ah it was overloaded...fixed}
Note that we made the dependence of $G(h)$ on $h$ explicit. This is because in general, the group defined in this way may depend on $h$, and not only on $\code$. If however we further impose all pairwise commutation relations then we obtain the following.

@@

Let $G_\bRM = G(h_\bRM)$ be the group that is presented from $h_\bRM$ (\hnote{added:} recall from \Cref{sec:pres-code} that codes give rise to group presentations). Explicitly, $h_\bRM$ is the parity check matrix that arises from the tester described in Figure~\ref{fig:bRM-tester}.

@@

We do not know if $G_\bRM = \Z_2^K$, with $K=t(d+1)^m$. Instead we modify the presentation $G(h_\bRM)$ by adding pairwise commutation relations in a similar manner as Lemma~\ref{lem:com-code}. Let 
\[ G(h_\bRM) \,=\, \big\langle x_1,\ldots,x_N \;:\; \{R^\sq_k\}\,,\; \{R^\ld_k\}\,,\; \{R^\had_{k}\} \big\rangle\;,\]
where  $R^\sq_k$ ranges overal all relations of the form $x_i^2=e$ for $i\in \{1,\ldots,N\}$, $R^\ld_k$ ranges over all relations implied by the ``low-degree test'' in Figure~\ref{fig:bRM-tester} and $R^\had_{k}$ ranges over all the relations implied by the ``Hadamard test.'' For $k=(i,j)\in\{1,\ldots,N\}$ such that $i<j$ let $R^\com_k$ be the relation $[x_i,x_j]=e$.
Then we define
\begin{equation}\label{eq:z2k-eff}
 G' \,=\,\big\langle x_1,\ldots,x_N \;:\; \{R^\sq_k\}\,,\; \{R^\ld_k\}\,,\; \{R^\had_{k}\}\, , \; \{ R^\com_k\}\big\rangle\;.
\end{equation}
From Lemma~\ref{lem:com-code} it follows that $G'=\Z_2^K$. Our main result is an efficient stability result for this presentation. To state this we need to introduce distributions $\mu_S$ and $\mu_R$ on the generators and relations of $G'$. The distribution $\mu_S$ is taken to be the uniform distribution over $[N] = (\F_2^t)^m \times \F_2^t$. The distribution $\mu_R$ is obtained as follows. With probability $1/4$ each, a relation from $\{R^\sq_k\}$, $\{R^\ld_k\}$ or $\{R^\had_k\}$ is chosen uniformly at random. With probability $1/4$, a random commutation relation from $R^\com_k$ is chosen according to the uniform mixture of the following two distributions:
\begin{enumerate}
\item For the first distribution, we select $u\in \F_q^m$ uniformly at random, $j\in\{1,\ldots,m\}$ uniformly at random, and $i\neq i'\in\{0,\ldots,d\}$ uniformly at random. Finally, select $\alpha,\beta\in \F_2^t$ uniformly at random and check commutation between $x_{u+i e_j,\alpha}$ and $x_{u+i' e_j,\beta}$. 
\item For the second distribution, we first select $j\in\{1,\ldots,m\}$ and $u_{m-j+2},\ldots,u_m \in \F_2^t$ uniformly at random. Then select $v,v' \in (\F_2^t)^m$ uniformly at random, conditioned on the last $(j-1)$ coordinates matching $u_{m-j+2},\ldots,u_m$. Finally, select $\alpha,\beta\in \F_2^t$ uniformly at random and check commutation between $x_{v,\alpha}$ and $x_{v',\beta}$.  \hnote{$v$ and $v'$ don't seem to show up, is it supposed to be $x_{v,\alpha}$ and $x_{v',\beta}$?}\tnote{yes, fixed}
\end{enumerate}

@@

\begin{proof}
Let $(\mM,\tau)$ be a tracial von Neumann algebra and $\phi$ be an $\eps$-homomorphism of $\langle S:R\rangle$ on $(\mM,\tau)$. 
 Here, $S = \{s_{u,\alpha}: u\in (\F_2^t)^m, \alpha\in \F_2^t\}$ \hnote{what is $s_{u,\alpha}$? should it be $x_{u,\alpha}$?}\tnote{Yes...this was a bit confusing. I added an ``explanation'' now}. We sometimes enumerate the items of $S$ as $S=\{x_i: i\in\{1,\ldots,N\}\}$, where $N=2^{tm+t}$ and we fixed an arbitrary bijection between $(\F_2^t)^m\times \F_2^t$ and $\{1,\ldots,N\}$. Let $R$ be the set of all relations in~\eqref{eq:z2k-eff}, i.e.\ $R= \{R_k^\sq\}\cup \{R^\ld_k\}\cup\{R^\had_k\}\cup\{R^\com_k\}$. Let $N=|S|$.

@@

\begin{claim}\label{claim:z2-stab-1}
There is an $\eps^{(1)}=O(d\eps)$ and an $\eps^{(1)}$-homomorphism $\phi^{(1)}$ of $\langle S:R\rangle$ on $(\mM,\tau)$ \hnote{same thing, should be $(\mM,\tau)$ I think}\tnote{yes} such that $\phi^{(1)}(x)$ is a Hermitian involution for all $x\in S$, and furthermore
\begin{equation}\label{eq:z2-stab-1a}
 \Es{x\sim\mu_S} \big\| \phi(x) - \phi^{(1)}(x) \big\|_\tau^2 \,\leq\, \eps^{(1)}\;.
\end{equation}
\end{claim}

\begin{proof}
Using elementary calculations (see e.g.~\cite[Lemma 3.6]{slofstra2019set}) we see that for any complex $\alpha$, 
\[ \big| \sgn\Re\alpha-\alpha\big| \,\leq\, \Big(1+\frac{1}{\sqrt{2}}\Big) \big|\alpha^2 -1 \big|\;.\]
For any $i\in \{1,\ldots,N\}$ let $\phi^{(1)}(x_i) = \sgn\Re (\phi(x_i))$ \hnote{maybe there should be a comment somewhere saying we identify $\{1,\ldots,N\}$ with $(\F_2^t)^m \times \F_2^t$}\tnote{see above}. Then the claim follows since 
\[ \Es{i\in\{1,\ldots,N\}} \big\| \phi(x_i)^2-\Id \big\|_\tau^2 \,\leq\, 4\eps\;,\]
by assumption and the definition of $\mu_R$, which places weight $\frac{1}{4}$ on the relations in $R_k^\sq$. Since $\mu_S$ is uniform on $S$,~\eqref{eq:z2-stab-1a} follows. Furthermore, because all relations in $R$ have length at most $O(d)$, $\phi^{(1)}$ is an $O(d\eps)$-homomorphism of $\langle S:R\rangle$\tnote{This requires more explanation, e.g.\ we need the marginal of any variable appearing in a relation to be uniform. I'm also not sure it's not $d^2$ instead of $d$.} \hnote{What is the length of a relation? The number of variables in it?}\tnote{yes}. 
\end{proof}

@@

\begin{claim}\label{claim:z2-stab-2}
Let $q=2^t$. 
For every $u\in \F_q^m$ there is a projective measurement $\{P^u_\alpha\}_{\alpha\in \F_{q}}$ on $\mM$ such that 
\begin{equation}\label{eq:z2-stab-2}
 \Es{u\in \F_q^m} \Es{\alpha\in \F_2^t} \Big\| \phi(s_{u,\alpha}) - \sum_{\beta\in\F_q} (-1)^{\alpha \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2 \,=\, O(\eps)\;. 
\end{equation}
\hnote{notational consistency: are we using $s_{u,\alpha}$ or $x_{u,\alpha}$?}\tnote{see above, is it ok now?}
\end{claim}

\begin{proof}
Since $\mu_R$ places weight $1/4$ on relations $\{R^\had_k\}$ we deduce that 
\begin{equation}\label{eq:stab-rm-1}
\Es{u\in \F_q^m} \Es{\alpha,\beta\in \F_2^t} \big\|\phi(s_{u,\alpha})\phi(s_{u,\beta})\phi(s_{u,\alpha+\beta})-\Id\big\|_\tau^2 \,\leq\, 4\eps\;. 
\end{equation}
Fix an $u\in \F_q^m$ and apply Lemma~\ref{lem:had-stab} for that $u$. This gives a partial isometry $w\in P\mM_\infty\Id_\mM$ and a unitary representation $\{U_\alpha\}$ of $\F_2^t$ on $\mN=P\mM_\infty P$ such that 
\begin{equation}\label{eq:stab-rm-1b}
 \Es{\alpha \in \F_2^t} \big\| \phi(s_{u,\alpha}) - w^* U_\alpha w \big\|_\tau^2 \,=\, O(\eps_u)\;,
\end{equation}
where $\eps_u\geq 0$ is such that $\Es{u\in \F_q^m} \eps_u = 4\eps$. Because $\{U_\alpha\}$ are a representation of the abelian group $\F_2^t$, there is a projective measurement $\{Q^u_\beta\}_{\beta\in \F_2^t}$ on $\mN$ such that $U_\alpha = \sum_\beta (-1)^{\alpha\cdot \beta} Q^u_\beta$. ($\{Q^u_\beta\}$ can be found explicitly by applying the Fourier transform, i.e.\ $Q^u_\beta = \sum_\alpha (-1)^{\alpha \cdot \beta} U_\alpha$.) Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{P^u_\beta\}_{\beta\in \F_q}$  \hnote{here (and in what follows) it's kind of confusing because $\beta$ keeps switching back and forth between $\F_q$ and $\F_q^t$, which means that sometimes it's $\kappa(\beta)$ and $\beta$, which is confusing...}\tnote{Ok so let's use $b$ for the $\F_2^t$ element} on $\mM$ such that (by the triangle inequality)
\begin{align*}
 \Es{\alpha \in \F_2^t} \Big\| \phi(s_{u,\alpha}) - \sum_{\beta\in\F_q} (-1)^{\alpha \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2
&\leq 2 \Es{\alpha \in \F_2^t} \Big( \Big\| \phi(s_{u,\alpha}) - w^*\Big(\sum_{b\in\F_2^t} (-1)^{\alpha \cdot b} Q^u_b \Big) w \Big\|_\tau^2 \\
&\qquad\qquad+   \Big\|  \sum_{b\in\F_2^t} (-1)^{\alpha \cdot b} w^* Q^u_b w - \sum_{\beta\in\F_q} (-1)^{\alpha \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2\Big)\\
 &\leq\, O(\eps_u) +  \sum_{\beta\in\F_q} \Big\| w^* Q^u_{\kappa(\beta)} w - P^u_{\beta} \Big\|_\tau^2\\
&\leq O(\eps_u)\;,
\end{align*}
where the first inequality follows from the triangle inequality, the second is by~\eqref{eq:stab-rm-1b} for the first term and Parseval's identity for the second, and the last by the guarantees obtained from Lemma~\ref{lem:pull-back}.
\end{proof}

>>>>

  A \emph{tracial von Neumann algebra} is a pair $(\mM,\tau)$ of a von Neumann algebra $\mM$ together with a normal faithful tracial state $\tau$ on $\mM$, which we often refer to as the \emph{trace}. The main example of interest is $\mM=M_n(\C)$, the algebra $n\times n$ complex matrices, with $\tau$ the dimension-normalized trace, which we denote $\tr(M)=\frac{1}{n}\Tr(M)$. 	We write $\|x\|_\tau=\tau(x^*x)^{1/2}$ to denote the $2$-norm on $\mM$ with respect to $\tau$. \hnote{sometimes we use $\| \cdot \|_\tau$ below, which one should we use?}\tnote{Ah yes sorry. I prefer $\|\cdot\|_\tau$} \hnote{edited}

@@

\begin{definition}\label{def:eff-stab}
Let $G = \langle S:R\rangle $ be a finitely presented group. Let $\mC$ be a class of tracial von Neumann algebras. Let $\mu_S$ be a distribution on $S$ and $\mu_R$ a distribution on $R$. For $\delta:[0,1]\to[0,1]$ such that $\lim_{t\to 0}\delta(t)=0$ we say that the presentation $G=\langle S:R\rangle$ is $(\delta,\mu_S,\mu_R,\mC)$-stable if for every $(\cM,\tau)$ in $\mC$, every $(\eps,\mu_R)$-almost homomorphism of $G$ is $(\delta(\eps),\mu_S)$-close to a unitary representation of $G$ on some $(\mN,\tau^\mN)\in \mC$. \tnote{added:} We refer to the function $\delta$ as the ``modulus of stability'' of the presentation.
\end{definition}

@@

\begin{theorem}\label{thm:gh}
Let $G$ be a finite group and $\mC$ the class of all tracial von Neumann algebras. Let $\mu_S$ and $\mu_R$ be the uniform distribution on $S=G$ and $R=\{ g\cdot h \cdot (gh)^{-1}=e \}$ respectively. Then $G=\langle S:R\rangle$ is $(O(\eps),\mu_S,\mu_R,\mC)$-stable.
\end{theorem}

@@

As one would naturally expect, the dependence of $\delta_k$ on $k$ depends on the girth of $\Z_2^k$ for the presentation~\eqref{eq:z2-efficient}. By expressing each element of $\Z_2^k$ as a product of generators in the natural way, applying Corollary~\ref{cor:lin-test} it is possible to show that $\delta_k=O(k^2\eps)$ in Lemma~\ref{lem:eff-z2}. With more work one can get $\delta_k=O(k\eps)$, see~\cite[Theorem 3.2]{chao2017overlapping}. This is nearly tight, as shown in~\cite{chao2017overlapping}. In the next section we will obtain presentations of $\Z_2^k$ that have a much better size/modulus tradeoff.

We end with a non-Abelian group that plays an important role in applications in quantum information, the \emph{Pauli group}. For an integer $k\geq 1$,  the Pauli group $\pauli_k$ can be defined as follows. Let $\gamma: \Z_2^k\times \Z_2^k \to \{-1,1\}$ be given by $\gamma(a,b)=(-1)^{a\cdot b}$. Then $\pauli_k$ is the central extension of $\Z_2^k\times \Z_2^k$ by $\{-1,1\}$ given by $\gamma$. Alternatively, $\pauli_k$ is the group generated by the Pauli matrices $\sigma_X(a)$, $\sigma_Z(b)$ introduced in~\eqref{eq:def-pauli-2}.
It is also known as the Heisenberg group 
\[ H_{2k+1} = \left \{ \begin{pmatrix} 1 & a & c \\ 0 & I_{k \times k} & b \\ 0 & 0 & 1 \end{pmatrix} \right\}\subseteq {\mathrm{GL}}_{k+2}(\F_2)\;.\]
 Concretely, %we label elements of the Pauli group as triples $(c,a,b)$ 
% where $c\in\{0,1\}$ and $a,b\in\Z_2^k$, and 
we consider the following presentation for the Pauli group:
\begin{align*}
 \pauli_k \,=\, \big\langle \{J\}\cup  \{(a,b): a,b\in \Z_2^k\} &: a^2=b^2=J^2=e,\; [a,J]=[b,J]=e,\\
&\qquad  (a,b)(a',b') = J^{a\cdot b'} (a',b')(a,b) \; \quad \forall a,b\big\rangle\;.
\end{align*}
This presentation is not quite the exhaustive presentation (it has $2^{2k}+1$ generators, whereas $|\pauli_k|=2^{2k+1}$), but it is not far from it.  
Applying Theorem~\ref{thm:gh} we obtain the following consequence.%, which we again state only for the case of a subclass of approximate homomorphisms and the class of finite-dimensional matrix algebras\tnote{again, not sure what we want ultimately}.

@@

For $q$ a prime power and $n,k,d$ integer, a linear $[n,k,d]_q$ code $\code$ is a $k$-dimensional subspace of $\F_q^n$ such that for all $x\in \code$ such that $x\neq 0$, the Hamming weight $|x|$ (i.e. the number of nonzero coordinates of $xs$) is at least $d$. The parameter $n$ is called the \emph{length} of the code, $k$ its \emph{dimension} and $d$ its \emph{distance}. A code can be specified by a \emph{parity check matrix} $h\in \F_q^{m\times n}$ such that $\code = \ker h$.

For the remainder of this section we specialize the discussion to the case where $q=2$. 
A parity check matrix for a code of dimension $k$ implies a presentation in the following way. Introduce $n$ generators $S=\{x_1,\ldots,x_n\}$. Each of the generators is required to be an involution: $x_i^2=e$. For each row $i\in \{1,\ldots,m\}$ of the parity check matrix $h$, introduce a relation 
\[ R_i\,:\; \prod_{1\leq j \leq n} x_j^{h_{ij}}=e \]
that ``verifies'' the parity check associated with the $i$-th row of $h$. Finally, to guarantee that $R_i$ is independent of the order in which the $x_j$ are multiplied, whenever $j\neq j'$ are such that $h_{ij}$ and $h_{ij'}$ are both nonzero we require that $x_j$ and $x_{j'}$ commute. This can be written succinctly using a relation 
\[ R'_{ijj'}\,:\; [x_j,x_{j'}]^{h_{ij} h_{ij'}}=e\;.\]
The presentation obtained in this way defines a group $G=G(h)$ as 
\begin{equation}\label{eq:def-gh-pres}
 G(h) \,=\, \big\langle x_1,\ldots,x_n \,:\, x_j^2=e\,,\; R_i\,,\; R'_{ijj'}\,,\quad \forall 1\leq i\leq m,\, 1\leq j< j' \leq n\big\rangle\;.
\end{equation}
Note that we made the dependence of $G(h)$ on $h$ explicit. This is because in general, the group defined in this way may depend on $h$, and not only on $\code$. If however we further impose all pairwise commutation relations then we obtain the following.

@@

Let $G_\bRM = G(h_\bRM)$ be the group that is presented from $h_\bRM$ (recall from \Cref{sec:pres-code} that codes give rise to group presentations). Explicitly, $h_\bRM$ is the parity check matrix that arises from the tester described in Figure~\ref{fig:bRM-tester}.

@@

We do not know if $G_\bRM = \Z_2^K$, with $K=t(d+1)^m$. Instead we modify the presentation $G(h_\bRM)$ by adding pairwise commutation relations in a similar manner as Lemma~\ref{lem:com-code}. Let 
\[ G(h_\bRM) \,=\, \big\langle x_1,\ldots,x_N \;:\; \{R^\sq_k\}\,,\; \{R^\ld_k\}\,,\; \{R^\had_{k}\} \big\rangle\;,\]
where  $R^\sq_k$ ranges overal all relations of the form $x_i^2=e$ for $i\in \{1,\ldots,N\}$, $R^\ld_k$ ranges over all relations implied by the ``low-degree test'' in Figure~\ref{fig:bRM-tester} and $R^\had_{k}$ ranges over all the relations implied by the ``Hadamard test.'' For $k=(i,j)\in\{1,\ldots,N\}$ such that $i<j$ let $R^\com_k$ be the relation $[x_i,x_j]=e$.
Then we define
\begin{equation}\label{eq:z2k-eff}
 G' \,=\,\big\langle x_1,\ldots,x_N \;:\; \{R^\sq_k\}\,,\; \{R^\ld_k\}\,,\; \{R^\had_{k}\}\, , \; \{ R^\com_k\}\big\rangle\;.
\end{equation}
From Lemma~\ref{lem:com-code} it follows that $G'=\Z_2^K$. Our main result is an efficient stability result for this presentation. To state this we need to introduce distributions $\mu_S$ and $\mu_R$ on the generators and relations of $G'$. The distribution $\mu_S$ is taken to be the uniform distribution over $[N] = (\F_2^t)^m \times \F_2^t$. The distribution $\mu_R$ is obtained as follows. With probability $1/4$ each, a relation from $\{R^\sq_k\}$, $\{R^\ld_k\}$ or $\{R^\had_k\}$ is chosen uniformly at random. With probability $1/4$, a random commutation relation from $R^\com_k$ is chosen according to the uniform mixture of the following two distributions:
\begin{enumerate}
\item For the first distribution, we select $u\in \F_q^m$ uniformly at random, $j\in\{1,\ldots,m\}$ uniformly at random, and $i\neq i'\in\{0,\ldots,d\}$ uniformly at random. Finally, select $\alpha,\beta\in \F_2^t$ uniformly at random and check commutation between $x_{u+i e_j,\alpha}$ and $x_{u+i' e_j,\beta}$. 
\item For the second distribution, we first select $j\in\{1,\ldots,m\}$ and $u_{m-j+2},\ldots,u_m \in \F_2^t$ uniformly at random. Then select $v,v' \in (\F_2^t)^m$ uniformly at random, conditioned on the last $(j-1)$ coordinates matching $u_{m-j+2},\ldots,u_m$. Finally, select $\alpha,\beta\in \F_2^t$ uniformly at random and check commutation between $x_{v,\alpha}$ and $x_{v',\beta}$. 
\end{enumerate}

@@

\begin{proof}
Let $(\mM,\tau)$ be a tracial von Neumann algebra and $\phi$ be an $\eps$-homomorphism of $\langle S:R\rangle$ on $(\mM,\tau)$. 
 Here, $S = \{s_{u,\alpha}: u\in (\F_2^t)^m, \alpha\in \F_2^t\}$. We sometimes enumerate the items of $S$ as $S=\{x_i: i\in\{1,\ldots,N\}\}$, where $N=2^{tm+t}$ and we fixed an arbitrary bijection between $(\F_2^t)^m\times \F_2^t$ and $\{1,\ldots,N\}$. Let $R$ be the set of all relations in~\eqref{eq:z2k-eff}, i.e.\ $R= \{R_k^\sq\}\cup \{R^\ld_k\}\cup\{R^\had_k\}\cup\{R^\com_k\}$. Let $N=|S|$.

@@

\begin{claim}\label{claim:z2-stab-1}
There is an $\eps^{(1)}=O(d\eps)$ and an $\eps^{(1)}$-homomorphism $\phi^{(1)}$ of $\langle S:R\rangle$ on $(\mM,\tau)$ such that $\phi^{(1)}(x)$ is a Hermitian involution for all $x\in S$, and furthermore
\begin{equation}\label{eq:z2-stab-1a}
 \Es{x\sim\mu_S} \big\| \phi(x) - \phi^{(1)}(x) \big\|_\tau^2 \,\leq\, \eps^{(1)}\;.
\end{equation}
\end{claim}

\begin{proof}
Using elementary calculations (see e.g.~\cite[Lemma 3.6]{slofstra2019set}) we see that for any complex $\alpha$, 
\[ \big| \sgn\Re\alpha-\alpha\big| \,\leq\, \Big(1+\frac{1}{\sqrt{2}}\Big) \big|\alpha^2 -1 \big|\;.\]
For any $i\in \{1,\ldots,N\}$ let $\phi^{(1)}(x_i) = \sgn\Re (\phi(x_i))$. Then the claim follows since 
\[ \Es{i\in\{1,\ldots,N\}} \big\| \phi(x_i)^2-\Id \big\|_\tau^2 \,\leq\, 4\eps\;,\]
by assumption and the definition of $\mu_R$, which places weight $\frac{1}{4}$ on the relations in $R_k^\sq$. Since $\mu_S$ is uniform on $S$,~\eqref{eq:z2-stab-1a} follows. Furthermore, because all relations in $R$ have length at most $O(d)$, $\phi^{(1)}$ is an $O(d\eps)$-homomorphism of $\langle S:R\rangle$\tnote{This requires more explanation, e.g.\ we need the marginal of any variable appearing in a relation to be uniform. I'm also not sure it's not $d^2$ instead of $d$.} 
\end{proof}

@@

\begin{claim}\label{claim:z2-stab-2}
Let $q=2^t$. 
For every $u\in \F_q^m$ there is a projective measurement $\{P^u_\alpha\}_{\alpha\in \F_{q}}$ on $\mM$ such that 
\begin{equation}\label{eq:z2-stab-2}
 \Es{u\in \F_q^m} \Es{\alpha\in \F_2^t} \Big\| \phi(s_{u,\alpha}) - \sum_{\beta\in\F_q} (-1)^{\alpha \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2 \,=\, O(\eps)\;. 
\end{equation}
\end{claim}

\begin{proof}
Since $\mu_R$ places weight $1/4$ on relations $\{R^\had_k\}$ we deduce that 
\begin{equation}\label{eq:stab-rm-1}
\Es{u\in \F_q^m} \Es{\alpha,\beta\in \F_2^t} \big\|\phi(s_{u,\alpha})\phi(s_{u,\beta})\phi(s_{u,\alpha+\beta})-\Id\big\|_\tau^2 \,\leq\, 4\eps\;. 
\end{equation}
Fix an $u\in \F_q^m$ and apply Lemma~\ref{lem:had-stab} for that $u$. This gives a partial isometry $w\in P\mM_\infty\Id_\mM$ and a unitary representation $\{U_\alpha\}$ of $\F_2^t$ on $\mN=P\mM_\infty P$ such that 
\begin{equation}\label{eq:stab-rm-1b}
 \Es{\alpha \in \F_2^t} \big\| \phi(s_{u,\alpha}) - w^* U_\alpha w \big\|_\tau^2 \,=\, O(\eps_u)\;,
\end{equation}
where $\eps_u\geq 0$ is such that $\Es{u\in \F_q^m} \eps_u = 4\eps$. Because $\{U_\alpha\}$ are a representation of the abelian group $\F_2^t$, there is a projective measurement $\{Q^u_b\}_{b\in \F_2^t}$ on $\mN$ such that $U_\alpha = \sum_b (-1)^{\alpha\cdot b} Q^u_b$. ($\{Q^u_b\}$ can be found explicitly by applying the Fourier transform, i.e.\ $Q^u_b = \sum_\alpha (-1)^{\alpha \cdot b} U_\alpha$.) Applying Lemma~\ref{lem:pull-back}, we deduce a projective measurement $\{P^u_\beta\}_{\beta\in \F_q}$ on $\mM$ such that (by the triangle inequality)
\begin{align*}
 \Es{\alpha \in \F_2^t} \Big\| \phi(s_{u,\alpha}) - \sum_{\beta\in\F_q} (-1)^{\alpha \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2
&\leq 2 \Es{\alpha \in \F_2^t} \Big( \Big\| \phi(s_{u,\alpha}) - w^*\Big(\sum_{b\in\F_2^t} (-1)^{\alpha \cdot b} Q^u_b \Big) w \Big\|_\tau^2 \\
&\qquad\qquad+   \Big\|  \sum_{b\in\F_2^t} (-1)^{\alpha \cdot b} w^* Q^u_b w - \sum_{\beta\in\F_q} (-1)^{\alpha \cdot \kappa(\beta)} P^u_\beta \Big\|_\tau^2\Big)\\
 &\leq\, O(\eps_u) +  \sum_{\beta\in\F_q} \Big\| w^* Q^u_{\kappa(\beta)} w - P^u_{\beta} \Big\|_\tau^2\\
&\leq O(\eps_u)\;,
\end{align*}
where the first inequality follows from the triangle inequality, the second is by~\eqref{eq:stab-rm-1b} for the first term and Parseval's identity for the second, and the last by the guarantees obtained from Lemma~\ref{lem:pull-back}.
\end{proof}
